%% adapted from Chris Bourke's syllabus template for CS 1
%% https://github.com/cbourke/ComputerScienceI
%% Accessed on 29 July 2020
%% Used and distributed under the CC BY-SA 4.0 License

\documentclass[12pt]{scrartcl}
%\usepackage{tagpdf}

\usepackage{epsfig,amssymb}

\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{multirow}
\usepackage{colortbl} 
\usepackage{xspace}
\usepackage[normalem]{ulem}

\usepackage{tcolorbox}

\definecolor{steelblue}{RGB}{70, 130, 180}
\definecolor{darkred}{rgb}{0.5,0,0}
\definecolor{darkgreen}{rgb}{0,0.5,0}
\usepackage[pdflang={en-US}]{hyperref}
\hypersetup{
  letterpaper,
  colorlinks,
  linkcolor=darkgreen,
  citecolor=darkgreen,
  menucolor=darkred,
  urlcolor=blue,
  pdfpagemode=none,
  pdftitle={Syllabus},
  pdfauthor={Dan DeBlasio},
  pdfkeywords={}
}
\setcounter{tocdepth}{2}

\usepackage{fullpage}
\pagestyle{empty} %
\usepackage{subfigure}
\usepackage{enumitem}
\setenumerate{nolistsep}
\setitemize{nolistsep}
\renewcommand{\labelenumii}{\alph{enumii}.}


\setlength{\parindent}{0pt} %
\setlength{\parskip}{.25cm}
\usepackage{lastpage}
\usepackage{fancyhdr}
\renewcommand*{\titlepagestyle}{fancy}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.4pt}

\lhead{~}
\chead{~}
\rhead{~}
\lfoot{\Title/DeBlasio -- Syllabus}
\cfoot{~}
\rfoot{\thepage\ / \pageref*{LastPage}}

\makeatletter
\title{Elementary Data Structures and Algorithms}\let\Title\@title
\subtitle{
{\small
Dr. Dan DeBlasio\\
Department of Computer Science\\
University of Texas at El Paso\\
}
\vskip-1cm}
\date{\small CS 2401 -- Fall 2022\\ \vspace{1em}Revised: \today\\(change since start of classes marked \change{}{in orange})}
\makeatother

\newcommand{\change}[2]{\textcolor{orange}{#2}}
%\newcommand{\change}[2]{#2}


%\tagpdfifpdftexT
% {
%  \pdfcatalog{/Lang (en-US)}
%  \usepackage[T1]{fontenc}
% }
% 
%\tagpdfsetup{activate-all,tabsorder=structure}

\begin{document}
%\tagstructbegin{tag=Document}

\maketitle
%
%\begin{center}
%{\Huge\color{red}DRAFT}
%\end{center}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{General Information}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\tagmcbegin{tag=P}
\paragraph{Course Objectives:} This is the second course for students majoring in Computer Science. Students will learn about fundamental computing algorithms including searching and sorting; recursion; elementary abstract data types including linked lists, stacks, queues and trees; and elementary algorithm analysis. 
%\tagmcend

\paragraph{Prerequisite:} CS 1301 and CS 1101 with a grade of C or better in both. 

\paragraph{Knowledge and Abilities Required Before Entering the Course:} Students are assumed to be comfortable programming in Java. Students should be able to code basic arithmetic expressions, define simple classes, use strings, code loops and conditional statements, write methods, create objects from classes, invoke methods on an object, perform basic text file input and output, and use arrays.

\paragraph{Topics covered this semester:}
\begin{itemize} 
\item Review and deeper study of arrays, objects, linked lists, and recursion. 
\item Introduction to algorithm analysis and rigorous study of searching and sorting algorithms. 
\item New data structures: binary trees (including binary search trees), stacks, and queues, along with their implementations. 
\end{itemize}

\clearpage
\tableofcontents

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Logistics}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Synchronous course session times and locations:}
\begin{itemize}
\item TR 3:00pm-4:20p (class) --- CCSB G.0208
\item TR 1:30pm-2:50p (lab) --- CCSB 1.0704
\end{itemize}

\paragraph{Template Weekly Assignments:} While each week of the course will be slightly different, and students should stay up to date, an ``average'' week in the course will include:
\begin{itemize}
\item 2 synchronous class sessions where the instructor will lead a discussion of examples and answer questions about the materials being learned
\item 2 synchronous lab sessions where the  instructional staff will lead a discussion primarily related to the lab assignments
\item 2 reading quizzes
\item 1-2 in-class/homework activities
\item 1 laboratory implementation assignment
%\item 1 group activity (lead by the peer leading staff) 
\end{itemize}

\paragraph{Textbook:} \textit{Introduction to Java Programming and Data Structures} by Y. Daniel Liang from Pearson Publishing. 
Available at \url{https://console.pearson.com/enrollment/css2dl}  (cost: \$90), 
or you can obtain a physical copy (ISBN: 978-0136520238). 
The textbook is \textbf{optional}, but recommended especially if you're not progressing adequately using only the course slides. 

\paragraph{Communication platforms:}
\begin{itemize}
\item \textbf{Blackboard} -- \href{http://cs2401.deblasiolab.org/f22/blackboard}{\texttt{cs2401.deblasiolab.org/f22/blackboard}}  -- Used for announcements and grade tracking. All official grades and feedback will be sent through Blackboard. Students should monitor this site for important class information. 
\item \textbf{MS Teams} -- \href{http://cs2401.deblasiolab.org/f22/teams}{\texttt{cs2401.deblasiolab.org/f22/teams}}  -- Used for office hours and intra-class discussions. Several channels will be available in the team for asking and answering questions, the instructional staff will answer questions posted on teams, but other students are encouraged to provide feedback as well. 
\item \textbf{Replit} -- \href{http://cs2401.deblasiolab.org/f22/replit}{\texttt{cs2401.deblasiolab.org/f22/replit}}  -- Used for lab assignments. Links to assignments will be posted, students are responsible for ensuring that assignments are committed correctly before the deadline. 
\item \textbf{YouTube} -- \href{http://cs2401.deblasiolab.org/f22/youtube}{\texttt{cs2401.deblasiolab.org/f22/youtube}} -- Used to disseminate asynchronous video content. Students will keep up with assigned video content intended to supplement the textbook readings.
\end{itemize}

\paragraph{Software: } 
Students will use the web-based Interactive Development Environment (IDE) \texttt{replit} to submit their assignments and get help from the instructional staff. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Instructional Staff}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{tabular}{lrl}
\multicolumn{3}{l}{\fontfamily{cmss}\selectfont \Large \textbf{Instructors}}\vspace{0.75em}\\
\textbf{Dr. Dan DeBlasio}  
 & email: & dfdeblasio@utep.edu\\
 & MS Teams: &  \href{http://cs2401.deblasiolab.org/dm}{\texttt{cs2401.deblasiolab.org/dm}} (direct message)\\
 & office: & CCSB 3.1008\\
& office hours:& tbd \\%& \href{http://cs2401.deblasiolab.org/f21/officehours}{\texttt{cs2401.deblasiolab.org/f21/officehours}}\\
%& & [or ``Office Hours'' on the class team]\\
& appointments: & \href{http://calendly.deblasiolab.org}{\texttt{calendly.deblasiolab.org}}\\

\\
\multicolumn{3}{l}{\fontfamily{cmss}\selectfont \Large \textbf{Teaching Assistants}}\vspace{0.75em}\\
%
Adeel Malik
 & email: & amalik@miners.utep.edu\\
 & office hours:&tbd \\%& \href{http://cs2401.deblasiolab.org/f21/officehours}{\texttt{cs2401.deblasiolab.org/f21/officehours}}\\
%
%
\\
\multicolumn{3}{l}{\fontfamily{cmss}\selectfont \Large \textbf{Instructional Assistants}}\vspace{0.75em}\\
%
Oswaldo Escobedo
 & email: & oescobedo3@miners.utep.edu\\
 & office hours:&tbd \\%& \href{http://cs2401.deblasiolab.org/f21/officehours}{\texttt{cs2401.deblasiolab.org/f21/officehours}}\\
 \\
Leonardo Munoz
 & email: & lemunoz4@miners.utep.edu\\
 & office hours:&tbd \\%& \href{http://cs2401.deblasiolab.org/f21/officehours}{\texttt{cs2401.deblasiolab.org/f21/officehours}}\\
%
%
\end{tabular}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Expectations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Communication:} Students are expected to consult their emails and blackboard messages \textit{at least} twice a week, and to answer these as relevant. 

\paragraph{Class and Lab Participation:} Keeping up with asynchronous content and participation in all synchronous class and lab sessions are critical factors of your success in this course. 

\textit{Students should be on time for all scheduled sessions and attend the entire session.} 
%Attendance will be taken at every synchronous class and lab session and will count towards your class participation grade. 
This semester attendance will not be taken to discourage those who may be sick to stay home, 
but those students who attend and readily participate in the course do better on assessments.

Students should notify the instructor prior to missing a session if at all possible, and certainly right after if earlier was not possible. 
%The instructor will allow two unexcused absences per semester before having the option to deduct points from the final grade (5 points per subsequent unexcused absence). 
Students should submit their work on time and meet all deadlines. Failing to do so will affect the participation grade.


\textit{It is the student's responsibility to review the content covered during missed class(es) or labs, as well as the assignments given during their absence.}
Participation points also include completing post-lecture and post-labs online quizzes (when requested) that are administered as surveys to monitor students’ overall progress and potential struggles.

\textit{Students should be on task.} 
When in synchronous class or lab session, students are expected to direct their attention to the task / activity as directed by the lecture / lab instructor. 
For instance, synchronous class sessions are certainly not places for social-networking, working on homework, participating in other courses.

\textit{Professionalism:} 
Students should be professional in their communications, as the context permits.
Emails should contains subjects, the recipients should be addressed (i.e. ``Hello Dr. DeBlasio, ...''), and the email should be signed with your name. 
Real-time online communication (i.e. MS Teams), while less formal, should still be professional. 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Grading}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Grades are communicated to students in a timely manner. 
It is the students’ responsibility to keep track of their grades by compiling the grades they receive. 
Your semester grade will be based on a combination of homework assignments, weekly quizzes, class participation, 4 mid-term assesments, student engagement, and a pair of  comprehensive exams. 

The approximate percentages are as follows:
\begin{center}
\begin{tabular}{rl}
\textbf{5\% } & Class participation \\
\textbf{15\% } & Homework/Quizzes/In-class assignments grade\\
\textbf{35\% } & Lab grade\\
\textbf{15\% } & Mid-term assessments (4 small tests, 1 class period) \\
\textbf{10\% } & Comprehensive in-class assessment (1 class period)\\
\textbf{20\% } & Final exam (up to 3 hours)\\
\end{tabular}
\end{center}
The base percentage-score-to-letter-grade conversion for CS 2401 is as follows: 

\begin{center}
\begin{tabular}{rl}
\textbf{90\%}& or higher is guaranteed an A \\
\textbf{80\%}& or higher is guaranteed a B \\
\textbf{70\%}& or higher is guaranteed a C \\
\textbf{60\%}& or higher is guaranteed a D \\
\textbf{}& all lower grades are an F 
\end{tabular}
\end{center}
These minimums may be lowered without notice but will not be raised. 

{\color{red} Important Note:} 
Regardless of your standing in the class at that time, you need to earn a C or better at the final exam to pass the course as well as a C or better as your average grade on the lab assignments. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Homework / Quizzes / In-class assignments}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Daily Quizzes}
The purpose of each quiz is to ensure that students are staying current with the weekly reading assignments and to verify that they have acquired the skills developed in class. 
Short quizzes are unannounced. 
All quizzes will be in person, 
%on blackboard, 
Quizzes are graded on submission not on correctness as a way to judge the progress of the student body, please try your best but note when you're making an educated guess. 

There will be no make-up on missed quizzes, but up to 3 quizzes can be dropped (missed) though the course of the semester.
 
 \subsubsection{Long Quizzes}
 Though the course of the semester we will have longer (graded) quizzes. 
 The modality of the quizzes will either be in class or online (to be determined). 
 They will be scheduled directly proceeding (the meeting before) each mid-term assessment and will cover similar material. 
 Details on these long quizzes will be announced in class as they occur. 
 
\subsubsection{In-class assignments}
There will be unannounced in-class assignments, to be turned in either by the end of the class or within a short period of time after the class (details will be given for each assignment). 
There will be no make-up for missed in-class assignments. 
Grades of such assignments will weigh equally with grades from quizzes. 

%\subsubsection{Online Homework} 
%You should expect to spend at least four hours per week outside of lecture on reading and homework. You should plan to devote extra four hours on your lab assignments. 
%Most of your homework will be work assigned on your online zyBooks: 
%a majority of deadlines are available at the start of classes on your zyBooks so that you can plan ahead;
%any additional zyBook homework will be announced in class and on blackboard. 
%Completing the assigned activities on time will be crucial to your success in the class (since these activities prepare you for classwork and exams). 
%Reading and homework assignments to be completed on your online textbook are usually meant to familiarize you with concepts that will be covered in depth in class. 
%If you struggle in any way while working on these, it is crucial that you seek help as soon as possible.
%Additional homework assignments will be announced in class and/or posted on blackboard (under the Timeline section of Resources).
%%If you miss a synchronous class session, it is your responsibility to find out what you missed, including assignments that might have been given.
%
%
%\paragraph{Online homework grade:} at each deadline, your instructor will collect your progress towards the due assignment. 
%The \% of completion you have achieved will be used to compute your grade on this particular homework. 

%\paragraph{Extra-credit opportunities:} 
%You will be given several opportunities to collect extra credit, to be applied to your homework grade (not to exceed an overall homework grade of 100\% on the online homework portion of your grade). 
%These opportunities will be clearly indicated in the list of deadlines in your online textbook. 
%There are three types of extra credit opportunities: catch-up homework, review homework, extra work, and professionalism.
%\begin{itemize}
%\item Catch-up homework assignments are regularly scheduled during the semester and are meant to help you make up some of the points you may not have made by the deadline of each individual homework assignment. 
%%\item Review homework: is a one-time opportunity. If you complete at least 75\% of the Review homework assignment (see zyBook for due date), you will receive 20 extra points to count towards your online homework grade (not to exceed 100 points total).
%%5\item Extra work: is also a one-time opportunity. If you complete at least 80\% of the Debugging and troubleshooting homework assignment (see zyBook for due date), you will receive 15 extra points to count towards your homework grade (not to exceed 100 points total).
%\item Professionalism: if all online homework was consistently completed on time, an extra 100 points will be assigned to the average making up the HW/Q/IC grade.
%\end{itemize}

\begin{tcolorbox}[colback=blue!5,colframe=blue!75!black,title=HW / Quizzes / In-Class Assignments Grade (HW/Q/IC)]
\begin{center}
Average (Daily Quizzes participation, Long Quiz grades, \\ other in-class assignments)\\
\end{center}
\end{tcolorbox}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Lab assignments and related homework}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Lab assignments are designed for you to further your practice on the concepts presented in class and demonstrate your level of mastery of these. 
In lab, you will typically work on either small activities related to currently covered concepts or concepts in which your instructional team thinks you should acquire more fluency, or more substantial lab assignments. 
Specifically, there will be approximately one lab assignments per week and a few smaller lab activities. 
%Online homework that is specific to the lab activities will be assigned: you will notice two assignments listed on your online zyBooks are labeled “Lab HW”. 
%Your completion of these will count towards your lab grade. 

%\paragraph{Other activities:} in lab, once a week on most weeks, you will participate in group-work during which you will solve problems. 
%You are expected to take an active part in these activities.

\paragraph{Attendance and active participation:} You are expected to attend and actively participate in labs (active participation includes the weekly group activities). 
%Attendance will be taken and will count towards your overall standing in the class.

Extra credit: there will be two extra-credit opportunities: 
\begin{itemize}
\item Extra lab at the end of the semester can be used to replace a previous lab assignment; and 
\item Attended office hours with three out of the 4 instructional staff (with a specific question, at least one must be with Dr. DeBlasio) and submit all labs on time (or within any pre-approved extension), an extra 100 point lab will be averaged into the lab assignments.
\end{itemize}

\paragraph{Grade:} Your grade for labs will be a combination of the grades you obtain at your lab assignments (90\%), your participation and performance on smaller activities, as well as your active participation in the problem-solving group activities (10\%). 
This grade will weigh 35\% of your overall CS2401 grade. 
You need to score 70\% or higher in labs to pass CS2401, regardless of your average otherwise.


\begin{tcolorbox}[colback=blue!5,colframe=blue!75!black,title=Lab Grade]
\begin{center}

Lab assignments (90\%) + \\
Attendance/Active Participation (10\%)
\end{center}

\end{tcolorbox}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Exams \& Assessments}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
There will be 4 small assessments through the semester, one final-prep exam, and one final exam. 
Because the exams contribute heavily to your total grade, it is vital that you do well on them. 
If you have test-taking difficulties in general, or if you have difficulties with our tests in particular, please request appropriate accommodation from UTEP’s Center for Accommodation and Students’ Services.

The purpose of the midterm assessments are to allow you to demonstrate mastery of course concepts covered thus far during the semester. 
Mid-term assessments will take place 
in class 
%on backboard with clear time constraints 
and are tentatively scheduled to be held in week 4, week 7, week 10, and week 13. 
Make-up exams will be given only in extremely unusual circumstances. 
If you must miss an exam, please meet with an instructor, \textit{BEFORE} the exam. 

{\color{red}Students are required to be on time for exams, a 10\% reduction to an exam grade will be made if a student arrives more than 5 minutes after the start of the test.
A 100\% deduction will be made after 15 minutes.}
Arriving to an exam late is disruptive to all students in the class and cannot be tolerated. 
 
\paragraph{Extra-credit opportunity:} 
for those students with (almost) perfect on-time homework (you can miss 1 deadline), a perfect grade of 100 will be added to the average making up the midterm exams grade.

\textbf{\underline{The final exam and comprehensive assessment will be comprehensive.}}
You must score 70\% or better on the final exam to pass this course. 
You must take the final exam during the time shown in the schedule for the lecture section that you normally attend. 
Do not "drop in" to another section: there will not be a copy of the exam for you. 
This is University policy. If you have a scheduling conflict (e.g., if you are taking a final at EPCC) or if you are scheduled for three final exams in one day, see your instructor at least a week in advance for arranging accommodation.
 The final exam will be held during exam week (all final exams schedules are also available online, on the UTEP website). 
 It is the students’ responsibility to keep informed.  
 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Standing in the course}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Special Assignments:} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
If deemed necessary, special assignments will be given to students to ensure that said students remain in the class and be successful. 
These will be designed to help students grow into the course and develop the necessary skills.
It is important that students feel free to ask their instructor about any such opportunity as well so that a special plan of development for CS2401 be tailored to them.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Standing in the Course:} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Students will have access to their grades for all assignments so that they can self-monitor their standing and progress. 
However, it is also completely fine for any student to come and talk to their instructor about their standing and work together to make sure the student is as successful as can be.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Dropping the Course:} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Every semester, some students drop the course. We, instructors, completely understand and respect that. We only hereby ask students to inform us, ideally before, but in the worst-case right after, of their intention to drop the course. This is really important for us as it possibly informs us of ways in which to better serve our students.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Special notices for COVID-19}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Please stay home if you have been diagnosed with COVID-19 or are experiencing COVID-19 symptoms. 
If you are feeling unwell, please let me know as soon as possible, so that we can work on appropriate accommodations. 
If you have tested positive for COVID-19, 
you are encouraged to report your results to covidaction@utep.edu, 
so that the Dean of Students Office can provide you with support and help with communication with your professors. 
The Student Health Center is equipped to provide COVID-19 testing. 
 
The Center for Disease Control and Prevention recommends that people 
in areas of substantial or high COVID-19 transmission wear face masks when indoors in groups of people. 
The best way that Miners can take care of Miners is to get the vaccine. 
If you still need the vaccine, it is widely available in the El Paso area, 
and will be available at no charge on campus during the first week of classes. 
For more information about the current rates, testing, and vaccinations, please visit epstrong.org.

\begin{tcolorbox}[colback=red!5,colframe=red!75!black,title=Masks in the classroom]
\textbf{To this end, until further notice the instrucional team and students are in the strongest terms possible
encouraged to wear a mask at all times in the classroom.}
If this is not possible, or you don't feel this is something that you want to do you're encouraged to transfer to another section of the course. 
\end{tcolorbox}

%While there is not a plan to hold any meetings of 2401 on campus this semester, 
%as the university updates it's campus operations there may be situations that lead a student to be on campus. 
%The following are a summary of the universities policies regarding COVID-19.
%
%You must STAY OFF CAMPUS and REPORT if you:
%(1) have been diagnosed with COVID- 19, 
%(2) are experiencing COVID-19 symptoms, or 
%(3) have had recent contact with a person who has received a positive coronavirus test. 
%Reports should be made at \href{http://screening.utep.edu}{\texttt{screening.utep.edu}}. 
%If you know anyone who should report any of these three criteria, encourage them to report. 
%If the individual cannot report, you can report on their behalf by sending an email to \url{COVIDaction@utep.edu}.
%
%For each day that you attend campus—for any reason—you must complete the questions on the UTEP screening website (\href{http://screening.utep.edu}{\texttt{screening.utep.edu}}) prior to arriving on campus. 
%The website will verify if you are permitted to come to campus. 
%Under no circumstances should anyone come to class when feeling ill or exhibiting any of the known COVID-19 symptoms. 
%If you are feeling unwell, please let me know as soon as possible, 
%and alternative instruction will be provided. Students are advised to minimize the number of encounters with others to avoid infection.
%
%Wear face coverings when in common areas of campus or when others are present. 
%You must wear a face covering over your nose and mouth at all times in this class. 
%If you choose not to wear a face covering, you may not enter the classroom. 
%If you remove your face covering, you will be asked to put it on or leave the classroom. 
%Students who refuse to wear a face covering and follow preventive COVID-19 guidelines will be dismissed from the class and will be subject to disciplinary action according to Section 1.2.3 Health and Safety and Section 1.2.2.5 Disruptions in the UTEP Handbook of Operating Procedures.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Resources}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Special Accommodations: }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
If you have a disability and need classroom accommodations, please contact the Center for Accommodations and Support Services (CASS) at 747-5148 or by email to cass@utep.edu, or visit their office located in UTEP Union East, Room 106. For additional information, please visit the CASS website at \href{http://www.sa.utep.edu/cass}{\texttt{www.sa.utep.edu/cass}}. CASS’ staff are the only individuals who can validate and if need be, authorize accommodations for students with disabilities.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Scholastic Dishonesty: }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Any student who commits an act of scholastic dishonesty is subject to discipline. Scholastic dishonesty includes, but not limited to cheating, plagiarism, collusion, and submission for credit of any work or materials that are attributable to another person.

Cheating is:
\begin{itemize}
\item Copying from the test paper of another student
\item Communicating with another student during a test to be taken individually
\item Giving or seeking aid from another student during a test to be taken individually
\item Possession and/or use of unauthorized materials during tests (i.e. crib notes, class notes, books, etc.)
\item Substituting for another person to take a test
\item Falsifying research data, reports, academic work offered for credit
\end{itemize}

Plagiarism is:
\begin{itemize}
\item Using someone’s work in your assignments without the proper citations
\item Submitting the same paper or assignment from a different course, without direct permission of instructors
\item[]\vspace{1em} To avoid plagiarism, see: \\{\footnotesize\url{https://www.utep.edu/student-affairs/osccr/_Files/docs/Avoiding-Plagiarism.pdf}}
\end{itemize}
                               
Collusion is:
\begin{itemize}
\item Unauthorized collaboration with another person in preparing academic assignments
\end{itemize}

\begin{tcolorbox}[colback=red!5,colframe=red!75!black,title=Important!]
When in doubt on any of the above, please contact your instructor to check if you are following authorized procedure. Also, please check the UTEP’s Handbook of Operating Procedures at: hoop.utep.edu. 
\end{tcolorbox}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Detailed Learning Outcomes}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{Level 3: Synthesis and Evaluation}
Level 3 outcomes are those in which the student can apply the material in new situations. This is the highest level of mastery. On successful completion of this course, students will be able to identify, implement and use the following data structures as appropriate for a given problem:
\begin{enumerate}
    \item Implement and use the following data structures to solve computational problems:
    \begin{enumerate}
        \item Linked lists
        \item Binary trees as linked structures
        \item Binary search trees as linked structures
        \item Stackes
        \item Queues
    \end{enumerate}
    \item Trace code that uses:
    \begin{enumerate}
    	\item Strings
	\item Single-value data types
	\item 1D and 2D arrays
	\item Reference-based data structures
	\item Iterative methods
	\item Recursive Methods
	\item Primitive vs. non-primitive data types
    \end{enumerate}
\end{enumerate}

\subsection*{Level 2: Application and Analysis}
Level 2 outcomes are those in which the student can apply the material in familiar situations, e.g., can work a problem of familiar structure with minor changes in the details. Upon successful completion of this course, students will be able to:
\begin{enumerate}
    \item Describe, implement, and use the following algorithms for:
    \begin{enumerate}
        \item Searching: linear and binary search.
        \item Sorting: merge sort, quicksort, and at least one quadratic sorting algorithm. 
    \end{enumerate}
    
    
    \item Use basic notions of algorithm complexity:
    \begin{enumerate}
        \item Use Big-O notation to describe the running time and memory requirements for an algorithm. 
        \item Determine the best- and worst-case behaviors of a simple algorithm.
    \end{enumerate}
        
    \item Use standard problem-solving techniques such as: problem decomposition, iteration, and recursion. 
\end{enumerate}

\subsection*{Level 1: Knowledge and Comprehension}
Level 1 outcomes are those in which the student has been exposed to the terms and concepts at a basic level and can supply basic definitions. On successful completion of this course, students will be able to:
\begin{enumerate}
   \item Demonstrate an understanding of the features of object-oriented languages (related to the implementation of data structures discussed in other objectives)
   \item Articulate the notion of average-case time complexity. 
\end{enumerate}


%\tagstructbegin{tag=Document}
\end{document}